\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-06-15 doc/USER_MANUAL/04_creating_databases.tex
added doc/USER_MANUAL/figures/how_to_use_a_transition_mesh_layer_to_stabilize_PML.png and some explanations

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly).

@@

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=6in]{figures/how_to_use_PML_when_a_tomographic_velocity_model_is_used.png}
\par\end{centering}

\caption{How to modify your external 3D velocity and density model in order
to use PML. Such a modification is not needed when using Stacey absorbing
boundary conditions (but such conditions are significantly less efficient).}

\label{fig:modify_external_velocity_model_to_use_PML}
\end{figure}

%%

>>>>

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly). \red{We have two utilities in directory utils/CPML that do that automatically
and that are very fast}. To stabilize PMLs it also helps to add a transition layer of geometrically-regular non-PML elements, in which attenuation is also 
turned off (i.e. $Q_\kappa = Q_\mu = 9999$ in that layer), as in the red layer of Figure~\ref{fig:mesh_extrusion}.
Our tools in directory utils/CPML implement that transition layer automatically.

@@

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=4.5in]{figures/how_to_use_a_transition_mesh_layer_to_stabilize_PML.png}
\par\end{centering}
\caption{Mesh extrusion for PML (green elements) and a non-PML stabilization layer (red elements).}
\label{fig:mesh_extrusion}
\end{figure}
%%

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=6in]{figures/how_to_use_PML_when_a_tomographic_velocity_model_is_used.png}
\par\end{centering}
\caption{How to modify your external 3D velocity and density model in order
to use PML. Such a modification is not needed when using Stacey absorbing
boundary conditions (but such conditions are significantly less efficient).}
\label{fig:modify_external_velocity_model_to_use_PML}
\end{figure}
%%
